Robust Subspace and Higher Moments Distances for Botnet Detection

### 2019-04-28 docs/papers/2019JNCA_m-rpca/2019JNCA_m-rpca.tex
working on introduction

Several efforts and reasearches aim to avoid network attacks based on known attackers, fingerprints or other kind of pattern. However, distributed attacks organized by botnet has increasing and demanding the development of counter measures in oder to detect and avoid unkown attacks or even to deal with adversarial changes of behavior, location and patterns, in order to avoid behavioral or pattern based detecion systems \cite{gu2008botminer, garcia2014empirical,khattak2015botflex,acarali2016survey,wang2017botnet,Wang2018ddosbotnetssurvey}. To face this problem, it is possible to adopt unsupervised or semi-pervised approches, where it is not necessary known anomalies for trannning models.

Anomaly detection is the identification of rare and suspicions observations by differing the normal or majority of the data. Anomalies can be related to network attack, fraud, defect or medical problems, for examples. Anomalies are also referred to as outliers, novelties, noise, deviations and exceptions. Anomalies can be hard to identify and separate from normal data.

Considering that anomalies are rare in comparison to normal events, anomaly detection algorithms have to deal with problems imposed by imbalanced data.

>>>>

Anomaly detection is the identification of rare and suspicions events by differing the normal or majority of the data. Anomalies are also referred to as outliers, novelties, noise, deviations or exceptions, and  can be related to network attack, fraud, defect or medical condiction, for examples \cite{bhuyan2014network,ahmed2016survey}. Anomalies can be hard to identify and separate from normal data due to the rare occurrencies of anomalies in comparison to normal events, therefore anomaly detection algorithms have to be robust, high discriminative and able to deal with the imbalanced data problem \cite{he2008learning}.

Several efforts and reasearches aim to avoid network attacks based on known attackers, fingerprints or other patterns. However, distributed attacks organized by botnet has increasing and demanding the development of counter measures in oder to detect and avoid unkown attacks or even to deal with adversarial changes of behavior, location and patterns, in order to avoid detection by behavioral or pattern based detecion systems \cite{gu2008botminer, garcia2014empirical,khattak2015botflex,acarali2016survey,wang2017botnet,Wang2018ddosbotnetssurvey}. To face this problem, it is possible to adopt unsupervised or semi-pervised approches, where it is not necessary known anomalies for trannning models \cite{moustafa2019holistic}.
